\pkg{DNest4}: An implementation of Diffusive Nested Sampling in \proglang{C++11} and \proglang{Python}

### 2016-05-10 paper/ms.tex
Keywords and shit

%% almost as usual
\author{Brendon J. Brewer\\The University of Auckland\And 
        Dan Foreman-Mackey\\Washington}
\title{\pkg{DNest4}: An implementation of Diffusive Nested Sampling in
C++11 and Python}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Brendon J. Brewer, Dan Foreman-Mackey} %% comma-separated
\Plaintitle{A Capitalized Title: Something about a Package foo} %% without formatting
\Shorttitle{\pkg{foo}: A Capitalized Title} %% a short title (if necessary)

@@

\Keywords{keywords, comma-separated, not capitalized, \proglang{C++11},
\proglang{Python}}
\Plainkeywords{keywords, comma-separated, not capitalized, Java} %% without formatting
%% at least one keyword must be supplied

>>>>

%% almost as usual
\author{Brendon J. Brewer\\The University of Auckland\And 
        Dan Foreman-Mackey\\Washington}
\title{\pkg{DNest4}: An implementation of Diffusive Nested Sampling in
\proglang{C++11} and \proglang{Python}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Brendon J. Brewer, Dan Foreman-Mackey} %% comma-separated
\Plaintitle{DNest4: An implementation of Diffusive Nested Sampling in
C++11 and Python} %% without formatting
\Shorttitle{\pkg{DNest4}: Diffusive Nested Sampling} %% a short title (if necessary)

@@

\Keywords{bayesian inference, markov chain monte carlo,
metropolis algorithm, bayesian computation, nested sampling, \proglang{c++11},
\proglang{python}}
\Plainkeywords{bayesian inference, markov chain monte carlo,
metropolis algorithm, bayesian computation, nested sampling, c++11, python} %% without formatting
%% at least one keyword must be supplied
